---
title: "without lags"
output: html_document
---

```{r setup, include=FALSE}

rm(list=ls())


library(tidyverse)
library(dplyr)
library(ggrepel)
library(knitr)
library(caret)
library(ranger)
library(glmnet)
library(e1071)
library(varImp)
library(MLeval)
library(DMwR)
library(ROSE)
library(MLmetrics)
library(mltools)
library(smotefamily)
#library(mlr)
#library(moments)
library(imbalance)
library(doParallel)





```

 

# Read in Cleaned Data Set
```{R}

CQD_final_set <- read.csv("CQD_final_set.csv")

```


Total Risk Based capital Ratio	(rbc1aaj)
Leverage ratio	(rbcrwaj)
Equity capital to assets	(eqv)
Net loans and leases to total assets	(lnlsntv)
Return on equity	(roe)
Return on assets	(roa)
Net operating income to assets	(noijy)
Net interest margin	(nimy)
Net Charge-offs to loans	(ntlnlsr)
Noninterest income to average assets	(noniiay)
Efficency Ratio	(eeffr)
Loan lease allowance to loans	(lnatresr)
Noncurrent assets plus other real estate	(nperfv)
Non-current loans to loans	(nclnlsr)
net loans and leases to core deposits	(idlncorr)
Cost of funding earning assets 	(intexpy)


# Functions for Macro F1
```{r}

# Precision Macro
Precision_macro <- function(y_true, y_pred, labels = NULL) {
  Confusion_DF <- ConfusionDF(y_pred, y_true)
  
  if (is.null(labels) == TRUE) labels <- unique(c(y_true, y_pred))

  
  Prec <- c()
  for (i in c(1:length(labels))) {
    positive <- labels[i]
    

    tmp <- Confusion_DF[which(Confusion_DF$y_true==positive & Confusion_DF$y_pred==positive), "Freq"]
    TP <- if (length(tmp)==0) 0 else as.integer(tmp)
    tmp <- Confusion_DF[which(Confusion_DF$y_true!=positive & Confusion_DF$y_pred==positive), "Freq"]
    FP <- if (length(tmp)==0) 0 else as.integer(sum(tmp))
    
    Prec[i] <- TP/(TP+FP)
  }
  Prec[is.na(Prec)] <- 0
  Precision_macro <- mean(Prec) 
  return(Precision_macro)
}

# Recall Macro

Recall_macro <- function(y_true, y_pred, labels = NULL) {
  Confusion_DF <- ConfusionDF(y_pred, y_true)
  
  if (is.null(labels) == TRUE) labels <- unique(c(y_true, y_pred))

  
  Rec <- c()
  for (i in c(1:length(labels))) {
    positive <- labels[i]
    

    tmp <- Confusion_DF[which(Confusion_DF$y_true==positive & Confusion_DF$y_pred==positive), "Freq"]
    TP <- if (length(tmp)==0) 0 else as.integer(tmp)
    
    tmp <- Confusion_DF[which(Confusion_DF$y_true==positive & Confusion_DF$y_pred!=positive), "Freq"]
    FN <- if (length(tmp)==0) 0 else as.integer(sum(tmp))
    
    Rec[i] <- TP/(TP+FN)
  }

  Rec[is.na(Rec)] <- 0
  Recall_macro <- mean(Rec)
  return(Recall_macro)
}


# F1_Score_Macro
F1_Score_macro <- function(y_true, y_pred, labels = NULL) {
  if (is.null(labels) == TRUE) labels <- unique(c(y_true, y_pred)) 
  Precision <- Precision_macro(y_true, y_pred, labels)
  Recall <- Recall_macro(y_true, y_pred, labels)
  F1_Score_macro <- 2 * (Precision * Recall) / (Precision + Recall)
  return(F1_Score_macro)
}


```



# Train Test Split | 2 Year Out of Time Split
```{r}
# Make Solvency a factor
CQD_final_set$solvency <- as.factor(CQD_final_set$solvency)



#Out of time validation set 
outoftime <- CQD_final_set[grepl(c("2014|2013"), CQD_final_set$date),]
outoftime <- outoftime %>%
        select(!c(date, cert))



# Train/Test set
TT <- CQD_final_set[!grepl(c("2014|2013"), CQD_final_set$date),]
TT <- TT %>%
        select(!c(date, cert))

table(TT$solvency)
table(outoftime$solvency)
sum(is.na(TT))
```



#Cartet Train Test split
```{r}

#Metrics
# ROC AUC
# Macro F-Meas (Only care about postives being picked correctly)
# Balanced Accuracy ( Cares if negatives and postives picked correctly)
# sensitivity TP/(TP/FN)
# Specificity
set.seed(111)

# Reverse Factor Levels
levels(TT$solvency) <- c("Solvent", "Insolvent")
TT$solvency <- factor(TT$solvency, levels=rev(levels(TT$solvency)))
                      
levels(outoftime$solvency) <- c("Solvent", "Insolvent")
outoftime$solvency <- factor(outoftime$solvency, levels=rev(levels(outoftime$solvency)))


train_split <- caret::createDataPartition(TT$solvency, p = 0.80, list = FALSE)
# Here we define a split index and we are now going to use a multiclass ML model to fit the data
train <- TT[train_split,]
test <- TT[-train_split,]


```

# Downsample Penalized Logistic Regression
```{r}
# Following prior Research I used AUROC for selecting the most efficient parameterization
#We employed the accuracy metric
#(AUROC) in the validation sub-sample for selecting the
#most efficient parameterization.

set.seed(111)

down_train <- downSample(x = train[, -ncol(train)],
                         y = train$solvency)

table(down_train$Class)

start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
ds_log = train(Class ~.,  
               data = down_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 100,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")


stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)

head(down_train)

# Probability Threshold
probs <- seq(.1, 0.9, by = 0.02)
ths <- thresholder(ds_log,
                   threshold = probs,
                   final = TRUE,
                   statistics = "all")
ths

ggplot(ths, aes(x = prob_threshold, y = J)) + 
  geom_point()


ggplot(ths, aes(x = prob_threshold, y = Sensitivity)) + 
  geom_point() + 
  geom_point(aes(y = Specificity), col = "red")


######################
# Confusion Matrix on Train Set
predictions <- predict(ds_log, down_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                down_train$Class))
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$down_train.Class)
cm
F1_Score_macro(predictions_1$down_train.Class, predictions_1$train_preds)
F_meas(predictions_1$train_preds, predictions_1$down_train.Class)
predictions <- predict(ds_log, down_train, type = "prob")
test1 <- evalm(data.frame(predictions, down_train$Class), positive = "Insolvent")


# Confusion Matrix on test Set
predictions <- predict(ds_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency, beta = 3)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(ds_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(ds_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency, beta = 3)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(ds_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")

?mcc

?F_meas

```
# OVer Sample With Replacement log reg
```{r}






?SMOTE


```


# Smote Log reg, TRY 50, 100, 200, 300, 400, 500, N
```{r}
# Need to play with Smote
set.seed(111)
smote_train <- SMOTE(solvency~., data = train)
table(smote_train$Class)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```



# Rose Log Reg
```{r}
?ROSE
set.seed(111)
rose_train <- ROSE(solvency~., data = train)$data
table(rose_train$solvency)

start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
rose_log = train(solvency ~.,  
               data = rose_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


# Probability Threshold
probs <- seq(.1, 0.9, by = 0.02)
ths <- thresholder(rose_log,
                   threshold = probs,
                   final = TRUE,
                   statistics = "all")
ths

ggplot(ths, aes(x = prob_threshold, y = J)) + 
  geom_point()


ggplot(ths, aes(x = prob_threshold, y = Sensitivity)) + 
  geom_point() + 
  geom_point(aes(y = Specificity), col = "red")

######################
# Confusion Matrix on Train Set
predictions <- predict(rose_log, rose_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                rose_train$solvency))

cm <- confusionMatrix(predictions_1$train_preds, predictions_1$rose_train.solvency)
cm
F_meas(predictions_1$train_preds, predictions_1$rose_train.solvency)
F1_Score_macro(predictions_1$rose_train.solvency, predictions_1$train_preds)
predictions <- predict(rose_log, rose_train, type = "prob")
test1 <- evalm(data.frame(predictions, rose_train$solvency), positive = "Insolvent")

# Confusion Matrix on Test Set
predictions <- predict(rose_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(rose_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")

# Confusion Matrix on out of time Set
predictions <- predict(rose_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(rose_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")

head(predictions_1)

```


# Adaptive Synthetic Sampling Approach (ADASYN)
```{r}






```



# Smote Modeling
###############################################################################################################################


# Default
#Smote No 200, Nu 200, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```


# Testing Number over 200
#Smote No 200, Nu 50, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 50)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```



#Smote No 200, Nu 75, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 75)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```



#Smote No 200, Nu 100, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 100)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```



#Smote No 200, Nu 150, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 150)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```


#Smote No 200, Nu 200, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 200)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```




#Smote No 200, Nu 250, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 250)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```


# Testing Number Over 100

#Smote No 100, Nu 50, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 50, perc.over = 100)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```
#Smote No 100, Nu 75, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 75, perc.over = 100)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```


#Smote No 100, Nu 100, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 100, perc.over = 100)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```


#Smote No 100, Nu 150, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 150, perc.over = 100)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```


#Smote No 100, Nu 200, k =5
```{r}
set.seed(111)
smote_train <- DMwR::SMOTE(solvency~., data = train, perc.under = 200, perc.over = 100)
table(smote_train$solvency)


start.time <- proc.time()
cl <- makePSOCKcluster(8)
registerDoParallel(cl, cores = 8)

set.seed(111)
smote_log = train(solvency ~.,  
               data = smote_train,
               method = "glmnet",
               trControl = trainControl(method = "cv", number = 10, classProbs = TRUE, savePredictions = TRUE, summaryFunction = twoClassSummary), 
               tuneLength = 10,
               preProcess = c("center", "scale"),
               family = "binomial",
               metric = "ROC")



stop.time <- proc.time()
run.time <- stop.time - start.time
print(run.time)
stopCluster(cl)


######################
# Confusion Matrix on Train Set
predictions <- predict(smote_log, smote_train, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                smote_train$solvency))
F_meas(predictions_1$train_preds, predictions_1$smote_train.solvency)
F1_Score_macro(predictions_1$smote_train.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$smote_train.solvency)
cm
predictions <- predict(smote_log, smote_train, type = "prob")
test1 <- evalm(data.frame(predictions, smote_train$solvency), positive = "Insolvent")


# Confusion Matrix on Test Set
predictions <- predict(smote_log, test, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                test$solvency))
F_meas(predictions_1$train_preds, predictions_1$test.solvency)
F1_Score_macro(predictions_1$test.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$test.solvency)
cm
predictions <- predict(smote_log, test, type = "prob")
test1 <- evalm(data.frame(predictions, test$solvency), positive = "Insolvent")


# Confusion Matrix on out of time Set
predictions <- predict(smote_log, outoftime, type = "raw")
predictions_1 <- cbind(data.frame(train_preds=predictions, 
                                outoftime$solvency))
F_meas(predictions_1$train_preds, predictions_1$outoftime.solvency)
F1_Score_macro(predictions_1$outoftime.solvency, predictions_1$train_preds)
cm <- confusionMatrix(predictions_1$train_preds, predictions_1$outoftime.solvency)
cm
predictions <- predict(smote_log, outoftime, type = "prob")
test1 <- evalm(data.frame(predictions, outoftime$solvency), positive = "Insolvent")


```







```



















